Patterns in Knowledge Production: Political Ruptures and Imperial Dynamics Shaping Public Discourse in Sweden and Finland, 1640–1828

### 2017-10-11 inst/examples/20170201-manuscript.Rmd
ok

# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)
```

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))  
  #   scale_color_stata() +
  #   scale_fill_stata() +
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = "black") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       ggtitle(paste("Average title length (", catal, ")", sep = "")) + 
       xlab("Year") +
       ylab("Title length (words)")
}

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
print(p)
```

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Year") +
       ylab("Publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs,
           labels = insert_minor(brs, 5, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     geom_bar(stat = "identity") +
     ggtitle("") +
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10)) +
     xlab("Year") +
     ylab("Title count (n)")

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, max(df$n), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Year") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +                                  
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Year") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(label = scientific_10) +
       ggtitle("Paper consumption on Octavo") +
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

```{r Fig15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
cat <- "Kungliga"

df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)

df1 <- df00 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat) %>%
	       group_by(publication_decade, publication_place)

df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
df1$publication_place <- droplevels(factor(df1$publication_place))

df1 <- df1 %>%
	       group_by(publication_decade, publication_place) %>% 
  	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

# Take cities from Fennica for Turku
cat <- "Fennica"

df2 <- df00 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat) %>%
	       group_by(publication_decade, publication_place)

df2$publication_place[!df2$publication_place == "Stockholm"] <- "Other"
df2$publication_place <- droplevels(factor(df2$publication_place))

df2 <- df2 %>%
	       group_by(publication_decade, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
                 mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

df <- bind_rows(df1, df2)
df$publication_place <- factor(df$publication_place)

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black",
         aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Year") +
       ylab("Title length (words)") +
       ggtitle("Mean title length") +
       scale_fill_stata() +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +          
       #scale_fill_manual(values = c("darkgray", "lightgray")) +       
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
catalogue <- "Fennica"
df <- filter(df0, catalog == "Fennica") %>%
  filter(publication_year >= 1640 & publication_year <= 1828) %>%
  select(publication_year, language, subject_topic)
df <- unique(df)
df <- df %>% group_by(publication_year, language) %>%
             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))

@@

brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
       ylab("Subject topics (n)") +
       xlab("Year") +
       ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))

>>>>

# Data with years limited as well
df0 <- df.full %>% filter(publication_year >= min.year & publication_year <= max.year)

cols <- list(Fennica = "blue", Kungliga = "darkred")
```

@@

  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))

  #p <- p + scale_fill_manual(values = c(cols[[catal]], "darkgray"))
  #p <- p + scale_color_manual(values = c(cols[[catal]], "darkgray"))

  #   scale_color_stata() +
  #   scale_fill_stata() +
  p <- p + xlab("Year")
  p <- p + ylab("Paper (sheets)")
  p <- p + ylim(c(0, max(na.omit(df2$paper))))

@@

pics <- list()
brs <- seq(min(decade(df$publication_year)), max(decade(df$publication_year)), 10)
brsy <- seq(0, round(max(na.omit(df$title_length)), -1), 10)
for (catal in unique(df$catalog)) {
  pics[[catal]] <- ggplot(subset(df, catalog == catal),
       aes(x = publication_year, y = title_length)) +
       geom_point(aes(size = n)) +
       geom_smooth(color = cols[[catal]], fill = cols[[catal]]) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 2), limits = c(0, max(na.omit(df$title_length)))) +
       ggtitle(paste("Median title length (", catal, ")", sep = "")) + 
       xlab("Year") +
       ylab("Title length (words)")
}

@@

# add the legend underneath the row we made earlier. Give it 10% of the height
# of one plot (via rel_heights).
p <- plot_grid( prow, legend_b, ncol = 2, rel_widths = c(1, .2))
# print(p)
```

@@

theme_set(theme_bw(20))
brs <- seq(min(npub$publication_decade), max(npub$publication_decade), 10)  
p <- ggplot(npub, aes(x = publication_decade, y = n)) +
       geom_bar(stat = "identity", position = "stack", color = "black",
       		    aes(fill = publication_place)) + 
       xlab("Year") +
       ylab("Publishers (n)") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs,
           labels = insert_minor(brs, 2, start = min(npub$publication_decade))) + 
       guides(fill = guide_legend(reverse = FALSE, title = "")) +
       ggtitle(paste("Publishers (", catal, ")", sep = ""))

@@

p <- ggplot(df, aes(x = publication_year, y = n)) +
     #geom_bar(stat = "identity") +
     geom_point() +
     geom_line(size = 1) +     
     ggtitle("") +
     scale_x_continuous(breaks = brs, labels = insert_minor(brs, 10, start = 1770)) +
     xlab("Year") +
     ylab("Title count (n)") +
     ggtitle(paste("Publications in Vaasa (", catalogue, ")", sep = ""))

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
brsy <- seq(0, round(max(df$n), -3), 1e3)
labs <- brs; labs[!brs %in% df$publication_decade] <- ""
p <- ggplot(df, aes(x = publication_decade, y = n)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Year") +
       ylab("Title count (n)") +
       ggtitle("Title count (absolute)") +
       #scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = labs) +
       scale_y_continuous(breaks = brsy, labels = insert_minor(brsy, 1)) +                                  
       guides(shape = guide_legend(title = "Place")) +
       guides(color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

df <- bind_rows(df1, df2)
brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place, shape = publication_place), size = 5) +
       xlab("Year") +
       ylab("Paper (sheets)") +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       scale_y_continuous(label = scientific_10) +
       ggtitle("Paper consumption (Octavo)") +
       guides(shape = guide_legend(title = "Place"), color = guide_legend(title = "Place")) +
       scale_color_stata()
print(p)
```

@@

```{r Fig15, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
df00 <- df.full %>% filter(publication_year >= 1640 & publication_year <= 1850)
df1 <- df00 %>% filter((publication_place %in% setdiff(cities, "Turku") & catalog == "Kungliga") |
                       (publication_place %in% "Turku" & catalog == "Fennica")) 
df1$publication_place[!df1$publication_place == "Stockholm"] <- "Other"
df1$publication_place <- droplevels(as.factor(as.character(df1$publication_place)))

df <- df1 %>% group_by(publication_decade, publication_place) %>%
  	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), 
	         mean_title_length = mean(title_length_wordcount, na.rm = TRUE))

brs <- seq(min(df$publication_decade), max(df$publication_decade), 10)
p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_bar(color = "black",
         aes(fill = publication_place), position = "dodge", stat = "identity") +
       xlab("Year") +
       ylab("Title length (words)") +
       ggtitle("Average title length") +
       scale_fill_stata() +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5, start = century(min(brs)) + 50)) +
       guides(fill = guide_legend(title = "Place", reverse = TRUE))        
print(p)
```

@@

```{r Fig17, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5, fig.show="hold"}
catalogue <- "Fennica"
df <- filter(df0, catalog == "Fennica") %>%
  filter(publication_year >= 1640 & publication_year <= 1828) %>%
  select(publication_decade, language, subject_topic)
df <- unique(df)
df <- df %>% group_by(publication_decade, language) %>%
             summarise(n = length(unique(unlist(strsplit(subject_topic, ";")))))

@@

brs <- seq(min(decade(df$publication_decade)), max(decade(df$publication_decade)), 10)

p <- ggplot(df, aes(x = publication_decade, y = n, shape = language)) +
       geom_line(size = 1, aes(color = language)) +
       geom_point(size = 4, aes(color = language)) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       # geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language"),
              color = guide_legend(title = "Language")) +
       scale_color_stata() +
       # scale_x_continuous(breaks = brs, labels = insert_minor(brs, 5)) +
       scale_x_continuous(breaks = brs, labels = insert_minor(brs, 2, start = century(min(brs)) + 40)) +                 
       ylab("Subject topics (n)") +
       xlab("Decade") +
       ggtitle(paste("Topic richness (", catalogue, ")", sep = ""))
